Analysis of split plot design using MCMCglmm

### 2018-11-04 README.Rmd
Fix badges and links (again)

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/adamhsparks/rice.awd.pests/commits/master)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/)
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) 
[![Travis-CI Build Status](https://travis-ci.org/openplantpathology/rice_awd_pests.svg?branch=master)](https://travis-ci.org/openplantpathology/rice_awd_pests)
[![Build status](https://ci.appveyor.com/api/projects/status/mh6s2n35fgry2hjo/branch/master?svg=true)](https://ci.appveyor.com/project/adamhsparks/rice-awd-pests-9lo9u/branch/master)

@@

The files at the URL above will generate the results as found in the
publication. The files hosted at
<https://github.com/openplantpathology/rice_awd_pests> are the development
versions and may have changed since the report was published.

@@

```
git clone https://github.com/openplantpathology/rice_awd_pests.git
```

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/adamhsparks/rice.awd.pests/commits/master)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/)
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) 
[![Travis-CI Build Status](https://travis-ci.org/adamhsparks/rice_awd_pests.svg?branch=master)](https://travis-ci.org/adamhsparks/rice_awd_pests)
[![Build status](https://ci.appveyor.com/api/projects/status/mh6s2n35fgry2hjo/branch/master?svg=true)](https://ci.appveyor.com/project/adamhsparks/rice-awd-pests-9lo9u/branch/master)

@@

The files at the URL above will generate the results as found in the
publication. The files hosted at
<https://github.com/adamhsparks/rice_awd_pests> are the development
versions and may have changed since the report was published.

@@

```
git clone https://github.com/adamhsparks/rice_awd_pests.git
```
